Baseline centering problem

### 2018-12-19 paper/tangotd.tex

Ideally, given the transition $s_3\to s'_3$, I'd like to sample $s_1$ and
$s_2$ proportionally to $Z$ (would cancel the $Z$ factors, and avoid
applying the equation to states that have nothing to do with
$s_3$—although the $Z$ factors are different for the three terms...). But
I don't know how to build an efficient sampler from $Z(s_3,\cdot)$.
Something like Metropolis? but this function $Z$ is not constant...
On-policy, sampling from $Z(\cdot,s_3)$ is easy: just sample one of the
recent states with geometric rates $\gamma$. This should divide the
equation by $Z(s_1,s_3)$ (up to some $\gamma$-dependent factor). I'm not
sure what to do with the resulting $Z(s_1,s_2)$. On-policy, another
option is to sample triplets $(s_1,s_3,s_2)$ that are some time apart on
the trajectory, e.g., starting with $s_3$ uniform along the past
trajectory, and moving back for $s_1$ and forward for $s_2$.

>>>>

Ideally, given the transition $s_3\to s'_3$, I'd like to sample $s_1$ and
$s_2$ proportionally to $Z$ (would cancel the $Z$ factors, and avoid
applying the equation to states that have nothing to do with
$s_3$—although the $Z$ factors are different for the three terms...). But
I don't know how to build an efficient sampler from $Z(s_3,\cdot)$.
Something like Metropolis? but this function $Z$ is not constant...
On-policy, sampling from $Z(\cdot,s_3)$ is easy: just sample one of the
recent states with geometric rates $\gamma$. This should divide the
equation by $Z(s_1,s_3)$ (up to some $\gamma$-dependent factor). I'm not
sure what to do with the resulting $Z(s_1,s_2)/Z(s_1,s_3)$. On-policy, another
option is to sample triplets $(s_1,s_3,s_2)$ that are some time apart on
the trajectory, e.g., starting with $s_3$ uniform along the past
trajectory, and moving back for $s_1$ and forward for $s_2$ (with factors
$\gamma$). Looks a lot like eligibility traces?
